Avoiding tipping points in fisheries management: A Bayesian Non-Parametric approach

### 2014-06-03 manuscripts/manuscript.Rmd
some edits from Steve

```{r libraries, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
library("nonparametricbayes") 
library("pdgControl")

@@

```{r sensitivity-trends}
source("components/sensitivity-trends.Rmd")
```

@@

In order to find that policy, we introduce the value function$V_t(x_t)$ representing the total discounted catch from time $t$ onwards given that $X_t=x$.  This value function satisfies an equation of Stochastic Dynamic Programming  [SDP, @Mangel1988; @Clark2000; @Clark2009], sometimes called the Bellman-Hamilton-Jacobi equation [@Mangel2014].

\begin{equation}
V_t(x) = \max_{h_t} \left[R(h_t, x_t) + \delta \cdot \mathbf{E}_{X_t+1} V_{t+1}( Z_{t+1} f(x - h_t)) \right]
\end{equation}

That is, at time $t$, when population size is $x$ and harvest $h_t$ is applied, the immediate return is $R(h_t, x_t)$ and the population size after the take is $x-h_t$, which is then translated into $X_{t+1}$ by Eqn 1. We consider the finite time problem with $T=$`r MaxT`, which we solve using value iteration algorithm [@Mangel1988; @Clark2000].

@@

A GP is an infinite dimensional (because it considers a continuous random
variable) stochastic process for which any realization is a multivariate
normal distribution. Thus, to characterize the GP we need a mean function
and a covariance matrix. We proceed as follows.

@@

$$y = f(x) + \varepsilon$$

$\varepsilon$ IID normal, variance $\sigma_n^2$. Then under the GP, the predicted data $X_p$ given the observations obeys

@@

plot_sigmas <- ggplot(vary_sigma, aes(noise, value)) + 
  geom_point() + ylab("Net present value") + 
  xlab("Level of growth stochasticity (sigma)") + theme_bw() 
plot_allees <- ggplot(vary_allee, aes(pars.C, value)) + 
  geom_point()+ ylab("Net present value") + 
  xlab("Allee threshold stock size") + theme_bw()
multiplot(plot_sigmas, plot_allees, cols=2)

>>>>

```{r libraries, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
library("knitr")
library("nonparametricbayes") 
library("pdgControl")

@@

```{r sensitivity-trends}
source("components/sensitivity-trends.R")
```

@@

In order to find that policy, we introduce the value function$V_t(x_t)$ representing the total discounted catch from time $t$ onwards given that $X_t=x$.  This value function satisfies an equation of Stochastic Dynamic Programming  [SDP, @Mangel1988; @Clark2000; @Clark2009], sometimes called the Bellman-Hamilton-Jacobi equation [@Mangel2014],

\begin{equation}
V_t(X_t) = \max_{h_t} \left{ R(h_t, X_t) + \delta \cdot \mathbf{\mathrm{E}}_{X_t+1} \left[ V_{t+1}( X_{t+1}) | X_t, h_t \right] \right}
\end{equation}

where expectation is taken over all possible values of the next state, $X_t{+1}$, and maximized over all possible choices of harvest, $h_t$.  That is, at time $t$, when population size is $x$ and harvest $h_t$ is applied, the immediate return is $R(h_t, X_t)$. In the classical case, the sole source of uncertainty is the process noise term, $Z$, and thus the expectation above is equivalent to taking expectations over $Z$. That is

$$ \mathbf{\mathrm{E}}_{X_t+1} \left[ V_{t+1}( X_{t+1}) | X_t, h_t \right] = \mathbf{\mathrm{E}}_{Z} \left[ V_{t+1}( Z f(X_t - h_t))  | X_t, h_t \right] $$

where the population size after the take is $X_t-h_t$, which is then translated into $X_{t+1}$ by Eqn 1.

In a Bayesian decision framework, the parameters governing the dynamics are also uncertain, so the
expectation in (1) involves averaging over the posterior distribution for the parameters, as well. That
is,

$$\mathbf{\mathrm{E}}_{X_t+1} \left[ V_{t+1}( X_{t+1}) | X_t, h_t \right] = \mathbf{\mathrm{E}}_{\theta,\mathrm{data}} \{ \mathbf{\mathrm{E}}_{Z | \theta, \mathrm{data}} \left[ V_{t+1}( Z f(X_t - h_t))  | X_t, h_t \right] \}$$

In the nonparametric case, the function $f$ too is uncertain and the expectation for the next state includes
uncertainty in $f$ as well. That is

$$\mathbf{\mathrm{E}}_{X_t+1} \left[ V_{t+1}( X_{t+1}) | X_t, h_t \right] = \mathbf{\mathrm{E}}_{\theta,\mathrm{data}} \{ \mathbf{\mathrm{E}}_{f, Z | \theta, \mathrm{data}} \left[ V_{t+1}( Z f(X_t - h_t))  | X_t, h_t \right] \}$$

We consider the finite time problem with $T=$`r MaxT`, which we solve using value iteration algorithm [@Mangel1988; @Clark2000].

@@

A GP is an infinite dimensional (because it is a function of a continuous input
variable) stochastic process for which any realization is a multivariate
normal distribution. Thus, to characterize the GP we need a mean function
and a covariance matrix. We proceed as follows.

@@

$$X_{t+1} = f(X_t) + \varepsilon$$

$\varepsilon$ IID normal, variance $\sigma_n^2$. Note that we have chosen to
assume additive noise.  While we could just as easily consider log-normal noise
as in the parametric models, we make this choice to bring home the point that the
Gaussian process approach need not have structurally correct noise form either.

Then under the GP, given a vector of observed data $X_0$ the predicted data $X_p$ obeys

@@

plot_sigmas <- ggplot(vary_sigma, aes(noise, value)) + 
  geom_point() + ylab("Net present value") + 
  xlab("Level of growth stochasticity (sigma)") + theme_bw() 
plot_allees <- ggplot(vary_allee, aes(pars.C, value)) + 
  geom_point()+ ylab("Net present value") + 
  xlab("Allee threshold stock size") + theme_bw()
cboettigR::multiplot(plot_sigmas, plot_allees, cols=2)

### 2014-06-03 manuscripts/manuscript.tex
some edits from Steve

\documentclass[author-year, 12pt,review]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}
\usepackage{lineno} % add 
  \linenumbers % turns line numbering on 
\bibliographystyle{elsarticle-harv}
\biboptions{sort&compress} % For natbib
\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%% Redefines the elsarticle footer
\makeatletter
\def\ps@pprintTitle{%
 \let\@oddhead\@empty
 \let\@evenhead\@empty
 \def\@oddfoot{\it \hfill\today}%
 \let\@evenfoot\@oddfoot}
\makeatother

% A modified page layout
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage{longtable}
\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Avoiding tipping points in fisheries management: A Bayesian Non-Parametric approach},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}
% Pandoc header

\begin{document}
\begin{frontmatter}

  \title{Avoiding tipping points in fisheries management: A Bayesian
Non-Parametric approach}
    \author[cstar]{Carl Boettiger\corref{c1}}
   \ead{cboettig@gmail.com} 
   \cortext[c1]{Corresponding author}
    \author[cstar]{Marc Mangel}

    \author[noaa]{Stephan Munch}

      \address[cstar]{Center for Stock Assessment Research, Department of Applied Math and
Statistics, University of California, Mail Stop SOE-2, Santa Cruz, CA
95064, USA}    
    \address[marc]{Center for Stock Assessment Research, Department of Applied Math and
Statistics, University of California, Mail Stop SOE-2, Santa Cruz, CA
95064, USA and Department of Biology, University of Bergen, Bergen,
Norway 9020}    
    \address[noaa]{Southwest Fisheries Science Center, National Oceanic and Atmospheric
Administration, 110 Shaffer Road, Santa Cruz, CA 95060, USA}

  \begin{abstract}
  Model uncertainty and limited data coverage are fundamental challenges
  to robust management of human intervention in a natural system. These
  challenges are acutely highlighted by concerns that many ecological
  systems may contain tipping points, such as Allee population
  sizes.\\Before a collapse, we do not know where the tipping points lie,
  if they exist at all. Hence, we know neither a complete model of the
  system dynamics nor do we have access to data in some large region of
  state-space where such a tipping point might exist. We illustrate how a
  Bayesian Non-Parametric (BNP) approach using a Gaussian Process (GP)
  prior provides a flexible representation of this inherent uncertainty.
  We embed GPs in a stochastic dynamic programming framework in order to
  make robust management predictions with both model uncertainty and
  limited data. We conduct a set of simulations to evaluate this approach
  as compared with the standard approach of using model selection to
  choose from a set of candidate models. We find that model selection
  erroneously favors models without tipping points -- leading to harvest
  policies that guarantee extinction. The GP approach performs nearly as
  well as the true model and significantly outperforms standard
  appraoches. We illustrate this using examples of simulated
  single-species dynamics, where the standard model selection approach
  should be most effective, and find that it still fails to account for
  uncertainty appropriately and leads to population crashes, while
  management based on the GP approach does not, since it does not
  underestimate the uncertainty outside of the observed data.
  \end{abstract}
   \begin{keyword} Bayesian \sep Structural Uncertainty \sep Nonparametric \sep Optimal Control \sep Decision Theory \sep Gaussian Processes \sep Fisheries Management \sep \end{keyword}
 \end{frontmatter}

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_1.pdf}
\caption{Points show the training data of stock-size over time. Curves
show the posterior step-ahead predictions based on each of the estimated
models. Observe that all models are fitting the data reasonably well.}
\end{figure}

@@

\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrr}
  \hline
 & Allen & Ricker & Myers \\ 
  \hline
DIC & 50.14 & 49.45 & 50.61 \\ 
  AIC & -24.60 & -30.07 & -27.19 \\ 
  BIC & -17.85 & -25.00 & -20.44 \\ 
   \hline
\end{tabular}
\caption{Model selection scores for several common criteria all (wrongly) select the simplest model. As the true (Allen) model is not distinguishable from the simpler (Ricker) model in the region of the observed data, this error cannot be avoided regardless of the model choice criterion. This highlights the danger of model choice when the selected model will be used outside of the observed range of the data.}
\end{center}
\end{table}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_2.pdf}
\caption{Graph of the inferred Gaussian process compared to the true
process and maximum-likelihood estimated process. Graph shows the
expected value for the function $f$ under each model. Two standard
deviations from the estimated Gaussian process covariance with (light
grey) and without (darker grey) measurement error are also shown. The
training data is also shown as black points. The GP is conditioned on
(0,0), shown as a pseudo-data point.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_3.pdf}
\caption{Outside the range of the training data (Figure 1), the true
dynamics (black dots) fall outside the uncertainty (two standard
deviations, colored bands) of the structurally incorrect parametric
models (Ricker, Myers), but inside the uncertainty predicted by the GP.
Points show the stock size simulated by the true model. Overlay shows
the range of states predicted by each model, based on the state observed
in the previous time step. The Ricker model always (wrongly) predicts
positive population growth, while the actual population shrinks in each
step as the initial condition falls below the Allee threshold of the
underlying model (Allen). Note that because it does not assume a
parametric form but instead relies more directly on the data, the GP is
both more pessimistic and more uncertain about the future state than the
parametric models.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_4.pdf}
\caption{The steady-state optimal policy (infinite boundary) calculated
under each model. Policies are shown in terms of target escapement,
$S_t$, as under models such as this a constant escapement policy is
expected to be optimal (Reed 1979).}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_5.pdf}
\caption{In the management context, GPDP outperforms approaches based on
parametric models. Shown are 100 replicate simulations of the stock
dynamics (eq 1) under the policies derived from each of the estimated
models, as well as the policy based on the exact underlying model.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_6.pdf}
\caption{Histograms of the realized net present value of the fishery
over a range of simulated data and resulting parameter estimates. For
each data set, the three models are estimated as described above. Values
plotted are the averages of a given policy over 100 replicate
simulations. Details and code provided in the supplement.}
\end{figure}

@@

(following the Ahrenius relationship, see Gardiner (2009) for the
derivation). As a result, the impact of using a model which
underestimates the risk of harvesting past the critical point is much
more severe, since this such a situation occurs more often. Conversely,
with large enough distance between the optimal escapement and unstable
points relative to the noise, the chance of a transition becomes
vanishingly small and all models can be modeled near-optimally. Models
that underestimate the cost incurred by stock sizes fluctuating
significantly below the optimal escapement level will not perform poorly
as long as those fluctuations are sufficently rare.

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_7.pdf}
\caption{Sensitivity Analysis. Histogram shows the ratio of the realized
net present value derived when managing under the GPDP over the optimal
value given the true model and true parameters. Values near 1 indicate
nearly optimal performance. Simulations cover a range of underlying
parameter, model, replicate, and noise levels.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_S1.pdf}
\caption{Traces from the MCMC estimates of the GP model show reasonable
mixing (no trend) and sampling rejection rate (no piecewise jumps)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_S2.pdf}
\caption{Posterior distributions from the MCMC estimate of the GP model.
Prior curves shown in red.}
\end{figure}

@@

All code used in producing this analysis can be found in the R package
accompanying the paper, available from
{[}http://github.com/cboettig/nonparametric-bayes{]}. The code for all
results shown here is dynamically embedded into the manuscript using
\texttt{knitr} (Xie 2012).

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_S3.pdf}
\caption{Traces from the MCMC estimates of the Ricker model show
reasonable mixing (no trend) and sampling rejection rate (no piecewise
jumps)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_S4.pdf}
\caption{Posteriors from the MCMC estimate of the Ricker model}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_S5.pdf}
\caption{Traces from the MCMC estimates of the Myers model show
reasonable mixing (no trend) and sampling rejection rate (no piecewise
jumps)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_S6.pdf}
\caption{Posterior distributions from the MCMC estimates of the Myers
model}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_S7.pdf}
\caption{Traces from the MCMC estimates of the Allen model show
reasonable mixing (no trend) and sampling rejection rate (no piecewise
jumps)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_S8.pdf}
\caption{Posteriors from the MCMC estimate of the Allen model}
\end{figure}

@@

>>>>

\documentclass[]{components/elsarticle}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
\usepackage{graphicx}
% Redefine \includegraphics so that, unless explicit options are
% given, the image width will not exceed the width of the page.
% Images get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\ScaleIfNeeded{%
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother
\let\Oldincludegraphics\includegraphics
{%
 \catcode`\@=11\relax%
 \gdef\includegraphics{\@ifnextchar[{\Oldincludegraphics}{\Oldincludegraphics[width=\ScaleIfNeeded]}}%
}%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Avoiding tipping points in fisheries management: A Bayesian Non-Parametric approach},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\title{Avoiding tipping points in fisheries management: A Bayesian
Non-Parametric approach}
\author{ \and  \and }
\date{}

\begin{document}

\begin{center}
\huge Avoiding tipping points in fisheries management: A Bayesian
Non-Parametric approach \\[0.2cm]
\normalsize
\end{center}

\begin{abstract}
Model uncertainty and limited data coverage are fundamental challenges
to robust management of human intervention in a natural system. These
challenges are acutely highlighted by concerns that many ecological
systems may contain tipping points, such as Allee population
sizes.\\Before a collapse, we do not know where the tipping points lie,
if they exist at all. Hence, we know neither a complete model of the
system dynamics nor do we have access to data in some large region of
state-space where such a tipping point might exist. We illustrate how a
Bayesian Non-Parametric (BNP) approach using a Gaussian Process (GP)
prior provides a flexible representation of this inherent uncertainty.
We embed GPs in a stochastic dynamic programming framework in order to
make robust management predictions with both model uncertainty and
limited data. We conduct a set of simulations to evaluate this approach
as compared with the standard approach of using model selection to
choose from a set of candidate models. We find that model selection
erroneously favors models without tipping points -- leading to harvest
policies that guarantee extinction. The GP approach performs nearly as
well as the true model and significantly outperforms standard
appraoches. We illustrate this using examples of simulated
single-species dynamics, where the standard model selection approach
should be most effective, and find that it still fails to account for
uncertainty appropriately and leads to population crashes, while
management based on the GP approach does not, since it does not
underestimate the uncertainty outside of the observed data.
\end{abstract}

\begin{verbatim}
## module glm loaded
\end{verbatim}

\begin{verbatim}
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
\end{verbatim}

\begin{verbatim}
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
\end{verbatim}

@@

\includegraphics{./manuscript_files/figure-latex/figure_1.pdf}

@@

\% latex table generated in R 3.1.0 by xtable 1.7-3 package \% Mon Jun 2
00:55:24 2014

\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
 & Allen & Ricker & Myers \\ 
  \hline
DIC & 50.75 & 50.45 & 50.41 \\ 
  AIC & -24.51 & -30.13 & -27.01 \\ 
  BIC & -17.75 & -25.06 & -20.25 \\ 
   \hline
\end{tabular}
\caption{Model selection scores for several common criteria all (wrongly) select the simplest model. As the true (Allen) model is not distinguishable from the simpler (Ricker) model in the region of the observed data, this error cannot be avoided regardless of the model choice criterion. This highlights the danger of model choice when the selected model will be used outside of the observed range of the data.} 
\end{table}

\includegraphics{./manuscript_files/figure-latex/figure_2.pdf}

@@

\includegraphics{./manuscript_files/figure-latex/figure_3.pdf}

\includegraphics{./manuscript_files/figure-latex/figure_4.pdf}

@@

\includegraphics{./manuscript_files/figure-latex/figure_5.pdf}

@@

\begin{verbatim}
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
\end{verbatim}

\includegraphics{./manuscript_files/figure-latex/figure_6.pdf}

@@

(following the Ahrenius relationship, see Gardiner (2009) for the
derivation). As a result, the impact of using a model which
underestimates the risk of harvesting past the critical point is much
more severe, since this such a situation occurs more often. Conversely,
with large enough distance between the optimal escapement and unstable
points relative to the noise, the chance of a transition becomes
vanishingly small and all models can be modeled near-optimally. Models
that underestimate the cost incurred by stock sizes fluctuating
significantly below the optimal escapement level will not perform poorly
as long as those fluctuations are sufficently rare. Figure 7 shows that
the GPDP is little effected by increasing noise or increasing Allee
effects over much of the range.

\begin{verbatim}
## Loading required package: grid
\end{verbatim}

\includegraphics{./manuscript_files/figure-latex/figure_7.pdf}

@@

\includegraphics{./manuscript_files/figure-latex/figure_S1.pdf}

\includegraphics{./manuscript_files/figure-latex/figure_S2.pdf}

@@

All code used in producing this analysis can be found in the R package
accompanying the paper, available from
{[}\url{http://github.com/cboettig/nonparametric-bayes}{]}. The code for
all results shown here is dynamically embedded into the manuscript using
\texttt{knitr} (Xie 2012).

\includegraphics{./manuscript_files/figure-latex/figure_S3.pdf}

\includegraphics{./manuscript_files/figure-latex/figure_S4.pdf}

@@

\includegraphics{./manuscript_files/figure-latex/figure_S5.pdf}

\includegraphics{./manuscript_files/figure-latex/figure_S6.pdf}

@@

\includegraphics{./manuscript_files/figure-latex/figure_S7.pdf}

\includegraphics{./manuscript_files/figure-latex/figure_S8.pdf}

@@

\begin{verbatim}
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
\end{verbatim}

\begin{verbatim}
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
\end{verbatim}

\includegraphics{./manuscript_files/figure-latex/figure_S9.pdf}
